The goal of a business evaluation is to get a comprehensive understanding of the organization's
strengths, weaknesses, opportunities, and threats (SWOT analysis)
in order to drive strategic decision-making and improve performance of the organization. 

\subsection{Critical Success Factor (CSF)}

A CSF represents a critical factor or activity that makes possible the successful execution of the processes of a company,
that is necessary to achieve the company's goal.

For a described online delivery service the CSF are the following:

\begin{itemize}
    \item Number of orders: the largest part of a revenue of a company comes from payments for orders.
    \item Time of delivery: since the goal of delivery is to provide goods for customers without clients spending time on going to a grocery store, the speed of delivery is sufficiently important for the service. Also fast delivery increases the possible number of orders per day.
    \item Quality of delivery: when it comes to a service, the customers need to have a good quality application, communication, and support.
    \item Application and a website platform quality: a stable app with user friendly UI helps to ensure that a customer will use it again.
    \item Quality of items provided: the quality of goods is sufficiently important because the delivered items will be used later by a client.
    \item Wide storage network: a strong connectivity between storages is a critical factor for a delivery service since it allows a courier to spend less time on the way to a storage and after to a client.
\end{itemize}

\subsection{Key Goal Indicators (KGI)}

KGI refers to an important long-term goal of a company that has to be achieved. Other metrics should lead to achieving this goal.

\begin{itemize}
    \item Increase the number of permanent users over time:
    This goal describes the overall number of people who used the service over a specific period of time. For example, the number of users in one month should be increased over time.
    \item Expand the delivery network:
    The delivery can be started in major cities but it can be extended to smaller cities and towns building the necessary connections and storage infrastructure for it.
    \item Expand the providers network:
Strong business partnership with goods providing companies helps to establish reliable suppliers with a good quality products
\end{itemize}

\subsection{Key Performance Indicators (KPI)}

These are important quantifiable indicators that lead to a desired goal.
It keeps focus on strategic improvement and helps to analyze the performance of a company.

\begin{itemize}
    \item Number of new clients over a period of time: success if increases.
    \item Number of orders over a period of time: success if increases.
    \item Average time spent to perform one order: success if decreases.
    \item Growth in revenue: success if increases.
    \item App rating in an app store: success if increases.
    \item Average delivery rating: success if increases.
    \item Number of new cities in a network: success if increases.
    \item Number of new storages in a network: success if increases.
    \item Number of orders performed by a courier over a period of time (courier’s performance): success if increases.
\end{itemize}
