When It comes to daily routine there are several services that have recently become a part of our life.
Business finds the way to explore new markets, improve logistics and use the modern advances of new technologies.
The example of these businesses that is going to be discussed in this work is a food delivery service.
Major chains of grocery stores all over the world apply digitalization in their business strategies and send products to the client’s address.
In 2023 the global food delivery market is worth \$150 billion according to McKincey. Examples of grocery chains using modern technology for delivery are Carrefour, Lidl and others. Popular food delivery services are Deliveroo, JustEat, UberEats and many others . Rapidly growing market leads to a competition between companies. It drives the development of technological products such as delivery apps, websites, customer services etc.

Here is the description and a short overview of a business model. Chain of grocery stores provides delivery service using website. Users can look for an item in a list of available products, add it to a bucket list, choose the delivery address and pay using online payment methods. Delivery person (courier) gets a task from the application, accepts it and goes to the closest storage of products dedicated to a company to fulfill the order. Once the order has completed, the courier reaches the destination address and gives the product to the user of the service. This is an example of the order to cash (O2C) process.

The processes in this model can be analyzed in order to improve the overall quality of the service.
The quality of a service from the client’s side can be measured using the following characteristics:

\begin{itemize}
    \item Delivery speed
    \item Quality of delivery
    \item Courier communication
    \item Quality of the app
    \item Packaging
    \item Sanitary requirements
    \item Support
    \item Overall customer satisfaction
\end{itemize}

The business side consists of the following parts:

\begin{itemize}
    \item Couriers and recruiting
    \item Product storages
    \item Couriers and assets tracking system
    \item Customer service
    \item Development and analytics office
    \item Maintenance
\end{itemize}

The tracking system helps to check the GPS location of a courier on the way to a customer, calculating the optimal route in a city. Other software capabilities are used In a product storage to optimize a picking up process. The optimal route between the racks can be calculated to decrease the overall time spent by a courier and improve the topology of a storage.

Everything has to be well incorporated in order to get the best results and win the competition on the market with the other companies.

In this work the processes with BPMN diagrams and business model will be discussed as well as the value model. Also the business evaluation will be provided with BPLE. The analysis of business leads to understanding of the steps that are necessary to be performed in order to improve the quality of the service and therefore increase the value and revenue of a business, solve problems and optimize the solutions.
